---
title: "830 Project"
author: "Leah Fowlkes (U02388955)"
date: "4/28/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r cars}
library(data.table)
library(purrr)
library(dplyr)
library(fixest)
library(broom)
# Read the data #
data <- fread('BA830-Project.csv')
```
```{r}
#Fixing a coding error
data %>% mutate (outcome_plate = recode (outcome_plate, '0' = 1, '1' = 0))
```



#Heterogeneous Treatment Effects
We will use the feols function to compute the heterogeneous treatment effect of being shown the red plate by whether the
person saw the food with the red plate on the left (first option) or right (second option) of the screen. 
```{r}
reg_het1 <- feols(outcome_plate ~ Treatment*outcome_food, data = data, se = 'white')
etable(reg_het1)
```

###Explanation of the Results
If a person only takes the treatment survey, they were more likely to pick the red plate 32.6% of the time than if they took the control survey. We also see if the food was on the left or listed as the first option, they were 20.8% more likely to pick the first option than the second. Lastly, if the person took the treatment survey and chose the first option of the survey, they were 33.4% less likely to pick the red plate. All of these results are a high significance level so we can believe these trends stand for 99% of the time. 



##We will use the feols function again to compute the heterogeneous treatment effect of being shown the red plate by whether the person saw a certain type or category of food. 

```{r}
reg_het2 <- feols(outcome_plate ~ Treatment*food_name, data = data, se = 'white')
etable(reg_het2)
```

###Explanation of the Results
For this regression, taking the treatment survey led people to choose the red plate 36.8% of the time more than if they took the control survey. There were 10 food categories: Burger, Dumpling, Fried Chicken, Fried Rice, Pasta, Salad, Salmon, Steak, Sushi, and Taco. Their respective treatment effects, with Burger standing as the 0 or the variable left out for the regression, were (-0.0417, 0.2083**, -0.0625, 0.2708***, 0.2708***, 0.0208, 0.2708***, 0.3125***, 0.2083** ).
Some of the food name effects were not at a high significance level so we will not report those. We see if Fried chicken or Taco was displayed, they were 21% more likely to choose the red plate option. For Pasta, Salad, and Steak, people tended to pick the red plate option for these meals 27% of the time more than the other option. People were 31% more likely to choose the red plate option if the food category was sushi.
Lastly, if people took the treatment survey and were shown a specific food category, the treatment effects are as follows: (0.1775, -0.3565***, 0.2106*, -0.4066***, -0.6412***, 0.1520, -0.3573***, -0.5594***, -0.1590). The fried chicken images led people to choose the red plate 36% of the time. Fried rice caused a 21% chance people would pick the red plate option. The pasta category crated a 21% higher chance the red plate option would be picked, while salad, steak, and sushi led to their red plate option being chosen -64%, -36%, and -56% of the time.  



#Limitations
Sample Size
One limitation to our regressions would be our sample size. Our sample only consisted of 186 survey results. This is not nearly enough observations to determine a trend on a larger scale so our statistical power is very low. Our probability of rejecting the null when there is a true treatment effect of some size is substantially low.


