---
output:
  pdf_document: default
  html_document: default
---
----
title: "BA 830 Project"
author: "Team 10"
date: "4/26/2021"
---
<style type="text/css">

body{ /* Normal  */
      font-size: 12px;
  }
td {  /* Table  */
  font-size: 8px;
}
h1.title {
  font-size: 24px;
  color: DarkRed;
}
h1 { /* Header 1 */
  font-size: 22px;
  color: DarkBlue;
}
h2 { /* Header 2 */
    font-size: 20px;
  color: DarkBlue;
}
h3 { /* Header 3 */
  font-size: 16px;
  font-family: "Times New Roman", Times, serif;
  color: DarkBlue;
}
code.r{ /* Code block */
    font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 14px;
}
</style>

Team members: Paula Demacker, Yuchen Feng, Leah Fowlkes, Ryan Veytsman, Xinping Yu, Yuzhe Zheng

# Introduction
Our goal is to determine if the color of the plate that the food is served on affects whether people want to eat the food. Then we can give some recommendations to restaurants to help them make better advertisements to attract more people. \
We created two surveys and used simple randomization to randomize at the person level to put each person into the treatment group or control group with different surveys. For each survey, we have basic demographic information such as gender, country and age group to see if any of this information may also affect the plate they choose. We also have 10 questions in each survey related to our experiment. In these questions, We asked people to select which food looks tastier based on the photos. We have ten different foods in total and for each question we display the same food but different food pictures on red or white plates. We randomized for each question if the red plate will be on the right or left and set the treatment survey opposite the plate color order for each question. We tested if people are more likely to choose the food based on the plate color, food itself or the position of the food.  


## Article: [COLOR PSYCHOLOGY: RED PLATES MAKE YOU EAT LESS](https://www.laweekly.com/color-psychology-red-plates-make-you-eat-less/)

### This article describes an experiment that found that when people eat off of red plates, they eat less than when eating from plates of any other color. Interestingly, this article provided two points of view. One was based on an experiment in Italy where the participants were given popcorn, chocolate, and hand cream. The study concluded that subjects took less of each thing than they did of the same thing on other plate colors. They theorized that people took less because red was associated with danger and prohibition. The second perspective suggested that red and green were actually more appetizing colors because they are found in nature and that the food on the plate looked less appetizing by contrast. 

## Article: [The effect of the color red on consuming food does not depend on achromatic (Michelson) contrast and extends to rubbing cream on the skin](https://pubmed.ncbi.nlm.nih.gov/23999521/)

### This article goes more into depth about the experiment described above with the popcorn, chocolate, and handcream. It found that although people used/took less of each product when it was on the red plate, they did not appreciate the product any less than when it was on the white or blue plate. 

## Article: [How Your Plate Affects Portion Size](https://www.profileplan.com/healthy-living/how-your-plate-affects-portion-size/)

### This article suggested that the color of the food and the contrast of the plate affected one's portion sizes because when the food had less contrast, the portion sizes people prefer would be smaller.  

```{r setup, include=FALSE, eval = TRUE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen=1, digits=3)
```

```{r, echo=FALSE}
#library
library(data.table)
library(tidyverse)
library(lfe)
library(fixest)
library(lubridate)
library(stargazer)
library(modelsummary)
```

```{r}
#import the file
food <- fread('BA830-Project.csv')
food = subset(food, select = -c(outcome_question)) #to get rid of extra column
food$outcome_plate.dummy <- ifelse(food$outcome_plate==0,1,0)  #to recode into new column properly
food$outcome_plate <- food$outcome_plate.dummy #to properly assign outcome_plate
food = subset(food, select = -c(outcome_plate.dummy)) #to rid of new extra column
```
```{r}
head(food)
```

```{r}
#data cleaning
#gender
food$gender_group[food$Gender == 'Man'] <- 1
food$gender_group[food$Gender == 'Woman'] <- 0
#age
food$age_group[food$Age == '16-25'] <- 1
food$age_group[food$Age == '26-35'] <- 2
food$age_group[food$Age == '36-45'] <- 3
food$age_group[food$Age == '46-55'] <- 4
food$age_group[food$Age == '56-65'] <- 5
#country
food$country_group[food$'Currently living' == 'Europe'] <- 1
food$country_group[food$'Currently living' == 'North America/Central America'] <- 2
food$country_group[food$'Currently living' == 'Asia/Middle east'] <- 3
food$country_group[food$'Currently living' == 'Australia/New Zealand'] <- 4
```
```{r}
#dimensions of the data
#Every respondent has 10 rows associated with their choices 
dim(food)
```
```{r}
#Distribution of responses based on Gender
food %>% count(Gender)
gender_order <- c('Man','Woman','Non-binary/third gender','Perfer not to say' )
ggplot(data = food, 
       aes(x = factor(Gender, level = gender_order))) + 
  geom_bar(color = '#2e2e2e' ,fill = '#04fbc4') + 
  scale_x_discrete(name = 'Gender', 
                   labels = c('Man' = 'Man', 
                              'Woman' = 'Woman', 
                              'Non-binary/third gender' = 'Non-binary/third gender', 
                              'Perfer not to say' = 'Prefer not to say')) 
```
## Distribution of responses based on Age
```{r, echo = FALSE}
#Distribution of responses based on Age
food %>% count(Age)
ggplot(data = food, aes(x = Age)) + geom_bar(color = '#2e2e2e' ,fill = '#04fbc4')
```
## Distribution of responses based on Region
```{r, echo = FALSE}
#Distribution of responses based on Region
food %>% count(country_group)
ggplot(data = food, aes(x = factor(country_group))) + 
  geom_bar(color = '#2e2e2e' ,fill = '#04fbc4') + 
  scale_x_discrete(name = 'Region', 
                   labels = c('1' = 'Europe', 
                              '2' = 'North America/Central America', 
                              '3' = 'Asia/Middle East', 
                              '4' = 'Australia/New Zealand')) 
```
## Distribution of responses based on choice of plate color
```{r, echo = FALSE}
#Distribution of responses based on choice of plate color
food %>% count(outcome_plate)
ggplot(data = food, aes(x = factor(outcome_plate))) + 
  geom_bar(color = '#2e2e2e' ,fill = '#04fbc4') + 
  scale_x_discrete(name = 'Plate Color', labels= c('0' = 'White', '1' = 'Red'))
```
## Distribution of responses based on Position of food
```{r, echo = FALSE}
#Distribution of responses based on Position of food
food %>% count(outcome_food)
ggplot(data = food, aes(x = factor(outcome_food))) + 
  geom_bar(color = '#2e2e2e' ,fill = '#04fbc4') + 
  scale_x_discrete(name = 'Food Position', labels= c('0' = 'Left', '1' = 'Right'))
```
## Distribution of responses based on treatment group
```{r, echo = FALSE}
#Distribution of responses based on treatment group
food %>% count(Treatment)
ggplot(data = food, aes(x = factor(Treatment))) + 
  geom_bar(color = '#2e2e2e' ,fill = '#04fbc4') + 
  scale_x_discrete(labels= c('0' = 'Control', '1' = 'Treatment'))
```
```{r}
food %>%
   group_by(food_name) %>%
   summarise(mean_plate = mean(outcome_plate),
             mean_food = mean(outcome_food))
```
From this we can see that on average, regardless of the food, the white plate was always preferred. This stands true regardless of if the food was on the right or on the left because although the average preferred food position varies on left or right preference for the specific food, the white plate was always preferred.
```{r}
treat <- food[, .(mean_outcome_pl = mean(outcome_plate)), by = .(Treatment,food_name)]

treat_1 <- treat[order(mean_outcome_pl)]

treat_1
```
On average, people in the control group picked the food on the red plate for Salmon, Burgers, Dumplings, and Fried rice more than on the white plate and people in the treatment group picked Salad on the red plate more often than on the white plate. Everyone else (people in treatment and control) picked all other foods most frequently on the white plates. 

```{r}
#proportion test
prop.test(nrow(food[Treatment ==  1])/10, nrow(food)/10, 0.5)
```
Our group is using simple randomization to select our treatment group and control group. By using the proportion test, we can see the p value here is 0.3 which is larger than 0.05, so we fail to reject the null hypothesis and prove that our experiment of treatment and control group was well randomized.

# Randomization / balance check for pre-experiment variables 
# between the treatment and control group.
```{r}
reg.age <- lm(age_group ~ Treatment, data = food)
summary(reg.age)
```

```{r}
reg.gender <- lm(gender_group ~ Treatment, data = food)
summary(reg.gender)
```

```{r}
reg.country <- lm(country_group ~ Treatment, data = food)
summary(reg.country)
```

```{r}
reg.plate <- lm(outcome_plate ~ Treatment, data = food)
summary(reg.plate)
```

```{r}
reg.question <- lm(outcome_food ~ Treatment, data = food)
summary(reg.question)
```

By running regressions for all the pre-experiment variables we selected based on our survey, we found out that gender_group and age_group gave us a p value bigger than 0.05 which is equal to 0.11 and 0.68 respectively. In this case, we are not able to reject the null hypothesis. It means that gender_group and age_group are well randomized between treatment group and control group. However, the p value for country_group is smaller than 0.05 which is 0.0096. In this case, we are able to reject the null hypothesis. It means that country_group is not well randomized between treatment group and control group. The reason for that is because we are using simple randomization, and the sample size for some countries is not big enough. For example, we only have three observations from Australia/New Zealand, and based on our simple randomization, it made our data have bias.

The last two regressions show that outcome_plate and outcome_food are both statistically significant which have p values equal to 5.4e-14 and 0.00048 respectively. Both of the variables are at the same significant level and the ate_hat for outcome_plate is -0.1737, and outcome_food is -0.0828. Since both the variables are at the three star significant level, we can conclude that outcome_plate has a bigger effect than outcome_food which means when people are picking their choice, they are more likely to choose based on the plate not the food.

# Regression 
```{r}
together <- feols(c(outcome_plate, outcome_food) ~ Treatment, 
                   data = food, se = 'white')
etable(together)
```
In the regression of model 1 we looked at the outcome_plate as the outcome variable first. We get an intercept of 0.4687, which represents the mean of the outcome of our control group. The estimate for the treatment effect is -0.1737 and has a standard error of 0.0227. Therefore, we have a negative treatment effect which indicates a negative relationship between Treatment and outcome_plate.\
We know from the three stars indicator that this result is statistically significant. This means that people in the treatment group are more likely to choose the white plate. 

For model 2 we used outcome_food as our outcome variable. The intercept is 0.4865. Our estimated treatment effect is -0.0828 and has a standard error of 0.0236. This indicates that we have a negative relationship between Treatment and outcome_food. These results are also statistically significant. The negative treatment effect shows us that people in the treatment group are more likely to choose the plate that is positioned on the left. 

```{r}
fixed_effects <- feols(outcome_plate ~ Treatment 
                  | outcome_food + food_name, data = food,
            se = 'white')
etable(fixed_effects)
```
For the regression above we added two fixed effects: outcome_food and food_name to see if the food has an impact on the outcome. The outcome variable is outcome_plate and has an estimated treatment effect of -0.1788 with an standard error of 0.0230, which is really similar to the regression above without the fixed effects. The results of this regression are also statistically significant and indicate that people in the treatment group are more likely to choose the food on the white plate. 

```{r}
reg.burger <- feols(outcome_plate ~ Treatment, data = food[food_name == 'Burger'])
reg.taco <- feols(outcome_plate ~ Treatment, data = food[food_name == 'Taco'])
reg.friedchicken <- feols(outcome_plate ~ Treatment, data = food[food_name == 'Fried Chicken'])
reg.salmon <- feols(outcome_plate ~ Treatment, data = food[food_name == 'Salmon'])
reg.pasta <- feols(outcome_plate ~ Treatment, data = food[food_name == 'Pasta'])
reg.steak <- feols(outcome_plate ~ Treatment, data = food[food_name == 'Steak'])
reg.dumpling <- feols(outcome_plate ~ Treatment, data = food[food_name == 'Dumpling'])
reg.sushi <- feols(outcome_plate ~ Treatment, data = food[food_name == 'Sushi'])
reg.friedrice <- feols(outcome_plate ~ Treatment, data = food[food_name == 'Fried Rice'])
reg.salad <- feols(outcome_plate ~ Treatment, data = food[food_name == 'Salad'])
etable(reg.burger,
       reg.taco, 
       reg.friedchicken, 
       reg.salmon, 
       reg.pasta, 
       reg.steak, 
       reg.dumpling, 
       reg.sushi, 
       reg.friedrice, 
       reg.salad)
```

```{r}
reg.europe <- feols(outcome_plate ~ Treatment, 
                    data = food[food$'Currently living' == 'Europe'])
reg.nc <- feols(outcome_plate ~ Treatment, 
                data = food[food$'Currently living' == 'North America/Central America'])
reg.am <- feols(outcome_plate ~ Treatment, 
                data = food[food$'Currently living'== 'Asia/Middle east'])
reg.an <- feols(outcome_plate ~ Treatment, 
                data = food[food$'Currently living' == 'Australia/New Zealand'])
etable(reg.europe, reg.nc, reg.am, reg.an)
```
All differences are significant except for people who are currently living in Australia/New Zealand. So we can say people in every country except Australia/New Zealand prefer white plates especially for people in the Asian region. 


# Heterogeneous Treatment Effects
We used the feols function to compute the heterogeneous treatment effects on choosing the red plate if the person took the treatment survey and chose the food displayed on the left (first option) on the screen.   
```{r}
reg_het1 <- feols(outcome_plate ~ Treatment*outcome_food, data = food, se = 'white')
etable(reg_het1)
```

### Explanation of the Results
For the heterogeneous treatment effect, if the person took the treatment survey and chose the first option of the survey, they were 33.4% more likely to pick the red plate. So the positioning of the answers for the choices may have had an impact on how many people chose the red plate. All of these results are at a high significance level so we can believe these trends stand most of the time. The combined treatment effect led more people to choose the red plate than the white plate. However, our other results from this regression indicate the treatment and the positioning of the food options on an individual level led to more people choosing the white plate over the red. 


## We will use the feols function again to compute the heterogeneous treatment effects on a person choosing the red plate if the person saw a certain category of food and took the treatment survey.  

```{r}
reg_het2 <- feols(outcome_plate ~ Treatment*food_name, data = food, se = 'white')
etable(reg_het2)
```

### Explanation of the Results
For the heterogeneous treatment effect, if people took the treatment survey and were shown a specific food category, the treatment effects are as follows: (-0.1775., 0.3565***, -0.2106*, 0.4066***, 0.6412***, -0.1520., 0.3573***, 0.5594***, 0.1590). The fried chicken images led people to choose the red plate more often by 36%. Fried rice caused a 21% lower chance people would pick the red plate option. The pasta category created a 41% higher chance the red plate option would be picked, while salad, steak, and sushi led to their red plate option being more likely chosen 64%, 36%, and 56% of the time. We only reported the variables with high significance levels ranging from a 90% confidence to 99% confidence. All heterogeneous treatment effects had a high significance level except Tacos.


# Limitations
### Sample Size 
One limitation to our regressions would be our sample size. Our sample only consisted of 178 survey results. This is not nearly enough observations to determine a trend on a larger scale so our statistical power is very low. Our probability of rejecting the null when there is a true treatment effect of some size is substantially low.
### Selection Bias
We gave out the survey through social media on Thursday and Friday. So those who were not able to use social media on those two days would not see our survey. The short experiment duration caused selection bias. Also, the age of our participants are primarily 16-25, which caused selection bias although it was well randomized. 
### Design of survey
From the pre-experiment check, we found different images of the food are also statistically significant. It is related to position preference as well. It is hard to figure out whether the different images or position preference exactly affect the outcome. 
### country not well randomized
The method we used for our experiment is simple randomization. This works for most observations, which are from Asia, North America and Europe. However, it was not well randomized due to the few observations from Australia and New Zealand. 

# Conclusion
### Suggestions for restaurant advertisement
As a result, our group will suggest restaurants to use white plates on their advertisements especially for dumpling, fried rice and salmon. Also, we strongly recommend restaurants in Asia to use white plate since it has the most significant differences and shows that people in Asia have a strong preference for white plates. Lastly, our main age group is people ages 16-25, so we strongly recommend the restaurants that want to attract young people follow our suggestions.







