----
title: "BA 830 Project"
author: "Team 10"
date: "4/26/2021"
output:
  pdf_document: default
  html_document: default
---
<style type="text/css">

body{ /* Normal  */
      font-size: 12px;
  }
td {  /* Table  */
  font-size: 8px;
}
h1.title {
  font-size: 24px;
  color: DarkRed;
}
h1 { /* Header 1 */
  font-size: 22px;
  color: DarkBlue;
}
h2 { /* Header 2 */
    font-size: 20px;
  color: DarkBlue;
}
h3 { /* Header 3 */
  font-size: 16px;
  font-family: "Times New Roman", Times, serif;
  color: DarkBlue;
}
code.r{ /* Code block */
    font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 14px;
}
</style>

Team members: Paula Demacker, Yuchen Feng, Leah Fowlkes, Ryan Veytsman, Xinping Yu, Yuzhe Zheng

# Introduction
Our goal is to determine if the color of the plate that the food is served on affects whether people want to eat the food. Then we can give some recommendations to restaurants to help them make better advertisement to attract more people. \
We created two surveys and used simple randomization to randomize by person level to put each person into treatment group or control group with different surveys. For each survey, we have basic demographic information such as gender, country and age group to see if any of this information may also affect the plate they chose. We also have 10 questions in each survey related to our experiment. In these questions, We asked people to select based on the photos which food looks tastier. We have ten different foods in total and for each question we display the same food but different food pictures into different colors of plate. We randomized for each question if the red plate will be on the right or left and set the treatment survey opposite the plate color order for each question. We will test if people are more likely to choose the food based on the plate color, food itself or the position of the answer.  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen=1, digits=3)
```

```{r, echo=FALSE}
#library
library(data.table)
library(tidyverse)
library(lfe)
library(fixest)
library(lubridate)
library(stargazer)
library(modelsummary)
```

```{r}
#import the file
food <- fread('BA830-Project.csv')
food = subset(food, select = -c(outcome_question)) #to get rid of extra column
food$outcome_plate.dummy <- ifelse(food$outcome_plate==0,1,0)  #to recode into new column porperly
food$outcome_plate <- food$outcome_plate.dummy #to properly assign outcome_plate
food = subset(food, select = -c(outcome_plate.dummy)) #to rid of new extra column
```
```{r}
head(food)
```

```{r}
#data cleaning
#gender
food$gender_group[food$Gender == 'Man'] <- 1
food$gender_group[food$Gender == 'Woman'] <- 0
#age
food$age_group[food$Age == '16-25'] <- 1
food$age_group[food$Age == '26-35'] <- 2
food$age_group[food$Age == '36-45'] <- 3
food$age_group[food$Age == '46-55'] <- 4
food$age_group[food$Age == '56-65'] <- 5
#country
food$country_group[food$'Currently living' == 'Europe'] <- 1
food$country_group[food$'Currently living' == 'North America/Central America'] <- 2
food$country_group[food$'Currently living' == 'Asia/Middle east'] <- 3
food$country_group[food$'Currently living' == 'Australia/New Zealand'] <- 4
```

```{r}
#proportion test
prop.test(nrow(food[Treatment ==  1])/10, nrow(food)/10, 0.5)
```
Our group is using simple randomization to select our treatment group and control group. By using the proportion test, we can see the p value here is 0.3 which is larger than 0.05, so we fail to reject the null hypothesis and prove that our experiment of treatment and control group was well randomized.

# Randomization / balance check for pre-experiment variables between the treatment and control group.
```{r}
reg.age <- lm(age_group ~ Treatment, data = food)
summary(reg.age)
```

```{r}
reg.gender <- lm(gender_group ~ Treatment, data = food)
summary(reg.gender)
```

```{r}
reg.country <- lm(country_group ~ Treatment, data = food)
summary(reg.country)
```

```{r}
reg.plate <- lm(outcome_plate ~ Treatment, data = food)
summary(reg.plate)
```

```{r}
reg.question <- lm(outcome_food ~ Treatment, data = food)
summary(reg.question)
```

By running regressions for all the pre-experiment variables of regression we selected based on our survey, we found out that gender_group and age_group gave us a big p value bigger than 0.05 which is equal to 0.11 and 0.68. In this case, we are not able to reject the null hypothesis. It means that gender_group and age_group are well randomized between treatment group and control group. However, the p value for country_group is smaller than 0.05 which is 0.0096. In this case, we are able to reject the null hypothesis. It means that country_group is not well randomized between treatment group and control group. The reason for that is because we are using simple randomization, and the sample size for some country is not big enough. For example, we might only have one observation from Country A, and based on our simple randomization, it will make our data be bias.

The last two regression shows that outcome_plate and outcome_food are both statistically significant which has p value equal to 5.4e-14 and 0.00048. Both of the variable are three star significant, the ate_hat for outcome_plate is -0.1737, and outcome_food is -0.0828. Since both the variable are at three star significant level, we can conclude that outcome_plate has a bigger effect than outcome_food which means when people are picking their choose, they are more likely choose based on the plate not the food.

# Regression 
```{r}
together <- feols(c(outcome_plate, outcome_food) ~ Treatment, 
                   data = food, se = 'white')
etable(together)
```
In the regression of model 1 we looked at the outcome_plate as the outcome variable first. We get an intercept of 0.4687, which represents the mean of the outcome of our control group. The estimate for the treatment effect is -0.1737 and has a standard error of 0.0227. Therefore, we have a negative treatment effect which indicates a negative relationship between Treatment and outcome_plate.\
We know from the stars that this result is statistically significant. This means that people in the treatment group are more likely to choose the white plate. 

For model 2 we used outcome_food as our outcome variable. The intercept is 0.4865. Our estimated treatment effect is -0.0828 and has a standard error of 0.0236. This indicates that we have a negative relationship between Treatment and outcome_food. These results are also statistically significant. It still indicates that people in the treatment group are more likely to choose the food on the red plate. The negtaive treatment effect shows us that people in the treatment group are more likely to choose the plate that is positioned on the right. 

```{r}
fixed_effects <- feols(outcome_plate ~ Treatment 
                  | outcome_food + food_name, data = food,
            se = 'white')
etable(fixed_effects)
```
For the regression above we added two fixed effects: outcome_food and food_name to see if the food has an impact on the outcome. The outcome variable is outcome_plate and has an estimated treatment effect of -0.1788 with an standard error of 0.0230, which is really similar to the regression above without the fixed effects. The results of this regression are also statistically significant.  


```{r}
reg.burger <- feols(outcome_plate ~ Treatment, data = food[food_name == 'Burger'])
reg.taco <- feols(outcome_plate ~ Treatment, data = food[food_name == 'Taco'])
reg.friedchicken <- feols(outcome_plate ~ Treatment, data = food[food_name == 'Fried Chicken'])
reg.salmon <- feols(outcome_plate ~ Treatment, data = food[food_name == 'Salmon'])
reg.pasta <- feols(outcome_plate ~ Treatment, data = food[food_name == 'Pasta'])
reg.steak <- feols(outcome_plate ~ Treatment, data = food[food_name == 'Steak'])
reg.dumpling <- feols(outcome_plate ~ Treatment, data = food[food_name == 'Dumpling'])
reg.sushi <- feols(outcome_plate ~ Treatment, data = food[food_name == 'Sushi'])
reg.friedrice <- feols(outcome_plate ~ Treatment, data = food[food_name == 'Fried Rice'])
reg.salad <- feols(outcome_plate ~ Treatment, data = food[food_name == 'Salad'])
etable(reg.burger,reg.taco, reg.friedchicken, reg.salmon, reg.pasta, reg.steak, reg.dumpling, reg.sushi, reg.friedrice, reg.salad)
```

```{r}
reg.europe <- feols(outcome_plate ~ Treatment, data = food[food$'Currently living' == 'Europe'])
reg.nc <- feols(outcome_plate ~ Treatment, data = food[food$'Currently living' == 'North America/Central America'])
reg.am <- feols(outcome_plate ~ Treatment, data = food[food$'Currently living'== 'Asia/Middle east'])
reg.an <- feols(outcome_plate ~ Treatment, data = food[food$'Currently living' == 'Australia/New Zealand'])
etable(reg.europe, reg.nc, reg.am, reg.an)
```
All differences are significant except for people who are currently living in Australia/New Zealand. So we can say people in every country except this have extremely habit on white plates especially for Asian people. 


# Heterogeneous Treatment Effects
We used the feols function to compute the heterogeneous treatment effects on choosing the red plate if the person took the treatment survey and chose the food displayed on the left (first option) on the screen.   
```{r}
reg_het1 <- feols(outcome_plate ~ Treatment*outcome_food, data = food, se = 'white')
etable(reg_het1)
```

### Explanation of the Results
For the heterogeneous treatment effect, if the person took the treatment survey and chose the first option of the survey, they were 33.4% more likely to pick the red plate. So the positioning of the answers for the choices may have had an impact on how many people chose the red plate. All of these results are at a high significance level so we can believe these trends stand for 99% of the time. The combined treatment effect led more people to choose the red plate than the white plate. However, our other results from this regression indicate the treatment and the positioning of the food options on an individual level led to more people choosing the white plate over the red. 


## We will use the feols function again to compute the heterogeneous treatment effects on a person choosing the red plate if the person saw a certain category of food and took the treatment survey.  

```{r}
reg_het2 <- feols(outcome_plate ~ Treatment*food_name, data = food, se = 'white')
etable(reg_het2)
```

### Explanation of the Results
For the heterogeneous treatment effect, if people took the treatment survey and were shown a specific food category, the treatment effects are as follows: (-0.1775, 0.3565***, -0.2106*, 0.4066***, 0.6412***, -0.1520, 0.3573***, 0.5594***, 0.1590). The fried chicken images led people to choose the red plate more often by 36%. Fried rice caused a 21% lower chance people would pick the red plate option. The pasta category created a 41% higher chance the red plate option would be picked, while salad, steak, and sushi led to their red plate option being more likely chosen 64%, 36%, and 56% of the time. We only reported the variable with high significance levels ranging from a 90% confidence to 99% confidence. Fried Chicken, Pasta, Salad, Steak, and Sushi were heterogeneous treatment effect categories we could have a 99% confidence in. The Fried Rice had a heterogeneous treatment effect we could have 90% confidence in.   



# Limitations
### Sample Size 
One limitation to our regressions would be our sample size. Our sample only consisted of 178 survey results. This is not nearly enough observations to determine a trend on a larger scale so our statistical power is very low. Our probability of rejecting the null when there is a true treatment effect of some size is substantially low.
### Selection Bias
We gave out the survey through social media on Thursday and Friday. So for those who were not able to use social media on those two days would not see our survey. The short time on experiment caused selection bias. Also, the age of our observations are primarily 16-25, which caused selection bias although it was well randomized. However, restaurants that aims to attract teenagers could use this information.
### Design of survey
From pre-experiment check, we found different dishes are also statistically significant. It is related to choice preference as well. Our result shows people tend to choose the right one in their survey. It is hard to figure out whether the different dished or choice preference exactly affect the outcome. To improve this, we could add one more treatment arm in our experiment.
### country not well randomized
The method we used for our experiment is simple randomization. This works for most observations, which are from Asia, North America and Europe. However, it was not well randomized due to the few observations from Australia and New Zealand. 

###Conclusion
#Suggestions for restaurant advertisement
As a result, our group will suggest restaurant to use white plate on their advertisement especially for dumpling, fried rice and salmon. Also, strongly recommend restaurants in Asia to use white plate since it has the most significant differences and shows that people in Asia have a strong preference for white plates.  






